---
title: "ST558_PROJECT2"
author: "Qiaozhi Bao"
date: "2020/10/6"
params:
  weekday: weekday_is_monday
output:
  rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=TRUE, eval=FALSE, echo=FALSE}
rmarkdown::render("README.Rmd.Rmd", output_file= "README.md")
```
# Introduction  
## Describe the data  
The [Online News Popularity data set]("https://archive.ics.uci.edu/ml/datasets/Online+News+Popularity") was published two years ago to summarize a heterogeneous set of features about articles published by Mashable in a period of two years.
There are 61 variables in total from the data set above: 58 predictive attributes, 2 non-predictive and 1 goal field.More details and summarization will be discussed later in this project.

##  The purpose of Analysis  

The purpose of this analysis is to create two models(ensemble and not ensemble) to generate the best predict of the response attribute--shares.Our analysis will help to determine what kind of content would be most popular.

## Methods  

For this project,I first split the data into training set and test set,then I examine the data with summary statistics and correlation plots to see the relationships between predictive attributes and the relationship between predictive attributes and response variables,then some meaningless variables were moved.
I then utilized the caret package to create two models.Tree-based model chosen using leave one out cross validation.Boosted tree model chosen using cross-validation.

# Data Study
## Description of the Used Data

As our study intention is to predict the popularity of an article, so we choose the shares as the response variable.After plotting the correlations between variables, we removed some high related predictive variables.
The two models were fitted by remaining variables in the training set. 

```{r,message=FALSE}
# Load all libraries
library(tidyverse)
library(ggplot2)
library(randomForest)
library(caret)
library(tree)
library(gbm)
library(corrplot)
library(e1071)
set.seed(1)
```
```{r}
# Read in data and removing the first two columns as they are not predictive variables.
news_pop <- read_csv('./OnlineNewsPopularity.csv') %>% select(-`url`,-`timedelta`)
params$weekday
```

```{r}
# First to see Monday data
data <- news_pop%>% select(!starts_with('weekday_is'),params$weekday)
# Check if we have missing values, answer is 'No'
sum(is.na(data))
data <-data %>% filter(data[,53]==1) %>%select(-params$weekday)
```

As there is no missing value in our Monday data, we will step to split data.
By using sample(), with 70% of the data goes to the training set (4,662 observations, Mon_train) and 30% goes to the test set (1,999 observations, Mon_test).

```{r}
# Split Monday data,70% for training set and 30% for test set
set.seed(1)
train <- sample(1:nrow(data),size = nrow(data)*0.7)
test <- dplyr::setdiff(1:nrow(data),train)
train_data <-data[train,]
test_data <- data[test,]
```
# Data Summarizations
## Predictor Variables   
I used the `summary()` function to calculate summary statistics for each of the quantitative variables in data.I divided the data into trunks to make plots easier to compare.

```{r}
summary(train_data)
correlation1 <- cor(train_data[,c(1:10,52)])
corrplot(correlation1,type='upper',tl.pos = 'lt')
corrplot(correlation1,type='lower',method = 'number',add = T,diag = F,tl.pos = 'n')
correlation2 <- cor(train_data[,c(11:20,52)])
corrplot(correlation2,type='upper',tl.pos = 'lt')
corrplot(correlation2,type='lower',method = 'number',add = T,diag = F,tl.pos = 'n')
correlation3 <- cor(train_data[,c(21:30,52)])
corrplot(correlation3,type='upper',tl.pos = 'lt')
corrplot(correlation3,type='lower',method = 'number',add = T,diag = F,tl.pos = 'n')
correlation4 <- cor(train_data[,c(31:40,52)])
corrplot(correlation4,type='upper',tl.pos = 'lt')
corrplot(correlation4,type='lower',method = 'number',add = T,diag = F,tl.pos = 'n')
correlation5 <- cor(train_data[,c(41:51,52)])
corrplot(correlation5,type='upper',tl.pos = 'lt')
corrplot(correlation5,type='lower',method = 'number',add = T,diag = F,tl.pos = 'n')
```

Unfortunately I did not find any variables are strongly related with the response,so my plan is remove some highly correlated predictive variables.
From the correlation plot,I decided to remove some meaningless variables:`is_weekend`,variables start with "LDA".
Also some highly correlated variables will be removed too,like variables start with"kw",then we will get a new train set and test set.  

```{r}
#Remove meaningless variables
train_data <- train_data %>% select(!starts_with("LDA"),-is_weekend)
test_data <- test_data %>% select(!starts_with("LDA"),-is_weekend)
train_data <- train_data %>% select(!starts_with('kw'))
test_data <- train_data %>% select(!starts_with('kw'))
```


# First Model
## Tree based model chosen using leave one out cross validation  

```{r}
tree.method <- train(shares ~.,data = train_data,method='rpart',
                       preProcess = c("center","scale"),
                     trControl = trainControl(method ='LOOCV'))
tree.method$results
tree.method$bestTune
```
# Second Model
## Boosted tree model chosen using cross-validation  

```{r}
# We will fit the model using repeated CV
boosted.method <- train(shares ~.,data = train_data,method = 'gbm',
                      trControl = trainControl(method = 'repeatedcv', number=5,repeats =2),
                      preProcess = c("center","scale"),
                      verbose = FALSE)

boosted.method$results
boosted.method$bestTune
```
## Compare RMSE 

We will make predictions using beset model fits and test set to compare the RMSE of the two models.We will choose the model with a smaller RMSE as our optimal model.

```{r}
# predict values on test set and compare RMSE for two models
pred.tree <- predict(tree.method,test_data)
pred.boost <- predict(boosted.method,test_data)
compare <- rbind(postResample(pred.tree,test_data$shares),postResample(pred.boost,test_data$shares))
rownames(compare)<-c("Tree method","Boosted method")
compare
```
We generates two very similar RMSE,the smaller is preferred.
In this case,we can see the boosted method generates smaller RMSE which is the same as we expected.The boosted method tend to have a better prediction than the tree based method.

